---
title: "Developing Data Products. Final assignment."
author: "Oscar BA"
date: "7/2/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Idea

Human activity has been affecting the environmental quality. It is important to do something to stop the current trend and take care of the environment.

The first step is to identify how are we polluting.

This app helps visualizing the Kyoto Greenhouse Gases emissions from 1950 to 2016.

## Data
The data was donwloaded from 'https://dataservices.gfz-potsdam.de/pik/showshort.php?id=escidoc:3842934'. Gutschow et al (2019) compiled several databases into one large dataset that includes pollution by country, year, pollutant and sector.

Gutschow, J., Jeffery, L., Gieseke, R., & Gunther, A. (2019). The PRIMAP-hist national historical emissions time series (1850-2017) [Data set]. GFZ Data Services. DOI:', 'https://doi.org/10.5880/PIK.2019.018'

```{r, eval=TRUE, echo=TRUE}
ghg <- read.csv('final/final_assignment/data/ghg.csv', na.strings = '.')
str(ghg)
```

## Trending
It can be seen that total greenhouse gases emissions are increasing.
```{r, message=FALSE, results='asis', cache=TRUE, echo=FALSE}
ghg_w <- ghg[ghg$country=='World' & ghg$sector=='Total',]
ghg_w <- ghg_w[!is.na(ghg_w$country),c(2,5,6,7,8)]
library(googleVis)
p <- gvisMotionChart(ghg_w, 'gas','year', options = list(width=600, height=400))
print(p, tag='chart')
```

## Conclusion
Check the final app and the plot of each country's emissions here: http://oscarba07.shinyapps.io/final_assignment

*Thank you*
 
